### 2015-06-26 reports/paper/conclusion.tex
thesis update

For future directions, one can extend the system with another microphone on each array to perform 3D localization. However, the number of grid points increases exponentially with the number of dimensions, which translates into exponential increase in computation time. To keep the localization in real time (time lag of less than $0.1$ seconds), it is important to research more efficient ways of finding the intersection of hyperbolic cones the in the 3D space. Since the likelihood calculation on each grid point is simply a look up on the cross-correlation output from each microphone pair, the computation at each grid point is independent of each other. Therefore, One straightforward way to speedup calculation is to employ hardware accelerated parallel computing technologies such as GPU or FPGA.

Another direction is to investigate multi-source localization. One approach is to allocate different frequency bands to difference sound sources. However, the number of frequency bands are limited in the audible audio spectrum, and our results showed that TDOA estimation is more accurate for a wide band signal compared to a narrow band signal. A different approach is to digitally encode and tag the audio source. Different sources can be differentiated if each source uses a waveform that has a different digital signature.

>>>>

For future directions, one can extend the system with another microphone on each array to perform 3D localization. However, the number of grid points increases exponentially with the number of dimensions, which translates into exponential increase in computation time. To keep the localization in real time (time lag of less than $0.1$ seconds), it is important to research more efficient ways of finding the intersection of hyperbolic cones the in the 3D space. Since the likelihood calculation on each grid point is simply a look up on the cross-correlation output from each microphone pair, the computation at each grid point is independent of each other. Therefore, one straightforward way to speedup calculation is to employ hardware accelerated parallel computing technologies such as GPU or FPGA.

Another direction is to investigate multi-source localization. One approach is to allocate different frequency bands to different sound sources. However, the number of frequency bands are limited in the audible spectrum, and our results showed that TDOA estimation is more accurate for a wide band signal compared to a narrow band signal. To allow signals to occupy the entire frequency band, one potential approach is to devise protocols that allow time division multiplex of source signals, where each source signal occupies a different time slot. Another approach is for each source to have a different audio signature. If the localization module knows all sources' audio signatures, it can use that information to recover each source signal from the received superimposed waveform.

### 2015-06-26 reports/paper/system.tex
thesis update

On the software side, \emph{Python} is used as the main programming language since it has extensive libraries in both real time data handling and signal processing. \emph{zeroMQ} is an inter process messaging queue that is used in our system to pass data across different modules. Our system is made up of two data acquisition modules (each is used to receive raw date from microphone array output) and one localization module (listens to both data acquisition modules and perform localization using the raw microphone data). Using \emph{zeroMQ} as connections to different modules adds flexibility to our system, as we can design applications such as the drawing application we have used in our system to interface only with the localization module and disregard how the microphone data is collected. Other localization applications can be easily integrated into our system by connecting them with the localization module. Furthermore, we have built a recording module that interfaces with the data acquisition modules for offline analysis and parameter tuning.

>>>>

On the software side, \emph{Python} is used as the main programming language since it has extensive libraries in both real time data handling and signal processing. \emph{ZeroMQ} is an inter process messaging queue that is used in our system to pass data across different modules. Our system is made up of two data acquisition modules (each is used to receive raw date from microphone array output) and one localization module (listens to both data acquisition modules and perform localization using the raw microphone data). Using ZeroMQ as connections to different modules adds flexibility to our system, as we can design applications such as the drawing application we have used in our system to interface only with the localization module and disregard how the microphone data is collected. Other localization applications can be easily integrated into our system by connecting them with the localization module. Furthermore, we have built a recording module that interfaces with the data acquisition modules for offline analysis and parameter tuning.
